### 2020-06-21 Report/aws_325ghz_study.tex
revised statistics Sreerekha et al

\subsection{Validation of simulations}
\label{sec:validation}
%
Using the simulation setup described above, around 77000 cases [* Is this the
correct final number? *] were simulated
based on randomly selected CloudSat orbits during August 2015. The input data
were restricted between $60^{\degree}$S to $60^{\degree}$N. No differentiation
was made between the observations over water and land.

\begin{figure}[p]
	\centering
	\includegraphics[height=60mm]{ATMS_C16_distribution}\hspace{5mm}% 
	\includegraphics[height=60mm]{ATMS_C17_distribution}
	\includegraphics[height=60mm]{ATMS_C18_distribution}\hspace{5mm}% 
	\includegraphics[height=60mm]{ATMS_C19_distribution}
	\includegraphics[height=60mm]{ATMS_C20_distribution}\hspace{5mm}% 
	\includegraphics[height=60mm]{ATMS_C21_distribution}
	\includegraphics[height=60mm]{ATMS_C22_distribution}
	\caption{Probability distribution functions (PDFs) of simulated and
      observed ATMS channels brightness temperatures for channels 16 - 22 and
      nadir viewing angle. The data covers latitude range $60^{\degree}$S to
      $60^{\degree}$N. Both land and ocean measurements are considered and only
      daytime ATMS data are included. See further the text.}
	\label{fig:pdf:c16-22}
\end{figure}

@@

In the intermediate region, the simulations have a lower occurrence rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citet{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher overrepresentation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresentated in the results.

\subsection{Dataset formed}
%
[* Describe here briefly the final set of simulations used below. Number of
cases, with and without thinng. Latiude range. If the full dataset was used for
ATMS comparsion, switch place between 3.3 and 3.4. Probably easiest to say that
all results below are for nadir. Otherwise this has to be clarified for the
simple scehem. *]

@@

\begin{figure}[!tb]
	\centering
	\includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The distribution of noise alone is also shown
      as reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The clear/cloudy classification is made with $dtb_{cs} = 1\sigma$ and also cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		noise                     &   0.00 &  0.63 &               0.00 &                - \\
		uncorrected-all           &  -0.75 &  4.62 &             -11.78 &                - \\
		corrected-linear model    &  -0.03 &  0.75 &               0.48 &                2.84 \\
		corrected-quadratic model &  -0.06 &  0.71 &              -0.34 &                2.84 \\
		corrected-cubic model     &  -0.05 &  0.72 &              -0.23 &                2.84 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation (std), and measure of skewness of error
      distributions shown in Figure~\ref{fig:correction:c34-42:fit}. The
      fraction rejected describes the percentage of cases which are removed.
      Results from three different fit models are shown: linear, quadratic and
      cubic.}
	\label{tab:correction:stats:34:42:allfits}
\end{table}
%
\begin{figure}[!tb]
  \centering \includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: noise
      (simulation dataset), uncorrected (thinned measurements), filtered $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are rejected), corrected $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are corrected), corrected
      $2\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 2$\sigma$ are corrected), Sreerekha et al (cloudy cases are filtered according to \citet{rekha2012potential}).}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
	uncorrected     		&  -1.27 &  6.05 &              -8.97 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\			
		\hline
\end{tabular}
\caption{Bias, standard deviation (std), and measure of skewness of the error
  distributions of datasets shown in
  Figure~\ref{fig:correction:c34-42:thinned}.}
\label{tab:correction:stats:34:42:thinned}
\end{table}

The distributions of filtered data are non-Gaussian. The right side of the
distribution follows measurement noise while the left side is skewed. The
skewness in the distribution is due to cloud impacts which pass through the
clear-sky threshold. The higher skewness in ``Sreerekha et al'' is mainly
beacuse their method only aims at removing cloud impacts above 4\,K.
Their approach also leads to a high rejection fraction (45.36\%). The filtering
method introduced here leads to a considerable lower rejection of data
(17.54\%).

@@

Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the
measurements to clear-sky values before and after correction, and the
corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
With clear/cloudy classification for $dtb_{cs} = 1\sigma$, around 85\% of the
total measurements are classified as cloudy and are rejected in pure-filtering.
Rejecting all the cloudy cases reduces the average bias in the measurements
from -2.25\,K to -0.21\,K, while with the approach from
\citet{rekha2012potential} only 45.36\% of the data is rejected and the average
bias reduces to -0.41\,K. When all the cloudy cases, except the ``too cloudy'',
are corrected, the total bias increases to 0.88\,K. The unusually high fraction
of cloudy cases and an increase in bias on correction suggests
misclassification of clear cases as cloudy. Since, the weighting functions of
AWS-32 and AWS-4X are poorly matched, their relationship is inadequate to
estimate the cloud impact in AWS-32. Without any additional information, the
regression approach can only provide a successful filtering in comparison to
the original approach described by \citet{rekha2012potential}, although at the
cost of high rejection fraction. Additional information seems necessary to improve
the accuracy of the correction.

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std & skewness & fraction \\
						&   [K]  &   [K] & [-] 		& rejected [\%]\\
		\hline
Noise             		&  0.00 &  0.45 &               0.01 &                - \\
uncorrected       		&  -2.25 &  8.94 &              -6.85 &                - \\
filtered($1\sigma$)  	&  -0.21 &  0.51 &              -0.65 &               85.43 \\
corrected($1\sigma$) 	&   0.88 &  1.76 &              -1.30 &                5.35 \\
corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.07 &                5.35 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for
      channel combinations: AWS-32 and AWS-4X. }
	\label{tab:correction:stats:32:4X}
\end{table}

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std & skewness & fraction \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		noise             		&   0.00 &  0.45 &               0.00 &                - \\
		uncorrected       		&  -2.25 &  8.94 &              -6.85 &                 - \\
		filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.33 &               72.06 \\
		corrected($1\sigma$) 	&   0.43 &  1.70 &             -14.68 &                7.93 \\
		corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.86 &                7.93 \\
		sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-32 and AWS-41.   }
	\label{tab:correction:stats:32:41}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &  skewness  & fraction\\
		&   [K]  &   [K] & [-]  & rejected [\%]\\
		\hline
		noise       	    	&  0.00 &  0.45 &               0.00 &               - \\
		uncorrected	    		&  -1.74 &  7.45 &              -7.77 &                - \\
		filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.18 \\
		corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.88 \\
		corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.88 \\
		sreerekha et al   		&  -0.29 &  0.78 &              -2.22 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-33 and AWS-41.   }
	\label{tab:correction:stats:33:41}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise           	  &  0.00 &  0.63 &               0.00 &                -\\
		uncorrected     	  &  -0.83 &  4.50 &             -10.85 &                - \\
		filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.30 \\
		corrected($1\sigma$)  &   0.01 &  0.90 &              -1.65 &                2.86 \\
		corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.35 &                2.86 \\
		sreerekha et al  	  &  -0.13 &  0.70 &              -0.54 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-35 and AWS-43.}
	\label{tab:correction:stats:35:43}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise            	 &  0.00 &  0.88 &              -0.01 &               - \\
		uncorrected      	 &  -0.54 &  3.40 &             -12.26 &                - \\
		filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.38 \\
		corrected($1\sigma$) &  -0.07 &  0.93 &              -0.07 &                2.50 \\
		corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
		sreerekha et al 	 &  -0.09 &  0.91 &              -0.10 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-36 and AWS-43.   }
	\label{tab:correction:stats:36:43}
\end{table}

@@

Table~\ref{tab:correction:stats:32:41} shows the statistics when AWS-32 is
corrected using AWS-41. The statistics of the filtered dataset are better than
the approach by \cite{rekha2012potential}, while the corrected data have poorer
statistics. This is not surprising as the weighting function match between
AWS-32 and AWS-41 is poor. The correction using $2\sigma$ as threshold works
better $1\sigma$. This is an exception, the reverse is valid for AWS-34/42 (as
mentioned) and the channel combinations discussed below.

>>>>

\subsection{Dataset formed}
%
Using the simulation setup described in previous section, we simulated 125460 cases based on randomly selected CloudSat orbits during August 2015. The input data
were restricted between $60^{\degree}$S to $60^{\degree}$N. We simulated both clear-sky and all-sky scenarios , and no differentiation was made between the observations over water and land. The simulations were generated for sensor viewing angles from $0^\circ$ to $45^\circ$, but all the results described in this report are based on nadir viewing angle.

Since in this study, the cases with cloud impact are extremely important, we used ``clear-sky thinning'' to improve the representation of the cloudy cases in the dataset. Thinned dataset is a subset of the full dataset with 50\% of the clear-sky cases removed. The size of the thinned dataset is different for each channel.

\subsection{Validation of simulations}
\label{sec:validation}
%
\begin{figure}[p]
	\centering
	\includegraphics[height=60mm]{ATMS_C16_distribution}\hspace{5mm}% 
	\includegraphics[height=60mm]{ATMS_C17_distribution}
	\includegraphics[height=60mm]{ATMS_C18_distribution}\hspace{5mm}% 
	\includegraphics[height=60mm]{ATMS_C19_distribution}
	\includegraphics[height=60mm]{ATMS_C20_distribution}\hspace{5mm}% 
	\includegraphics[height=60mm]{ATMS_C21_distribution}
	\includegraphics[height=60mm]{ATMS_C22_distribution}
	\caption{Probability distribution functions (PDFs) of simulated and
      observed ATMS channels brightness temperatures for channels 16 - 22 and
      nadir viewing angle. The data covers latitude range $60^{\degree}$S to
      $60^{\degree}$N. Both land and ocean measurements are considered and only
      daytime ATMS data are included. See further the text.}
	\label{fig:pdf:c16-22}
\end{figure}

@@

In the intermediate region, the simulations have a lower occurrence rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citet{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher overrepresentation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresented in the results.

@@

\begin{figure}[!tb]
	\centering
	\includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The distribution of noise alone is also shown
      as reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The clear/cloudy classification is made with $dtb_{cs} = 1\sigma$ and also cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		noise                     &   0.00 &  0.63 &               0.00 &                - \\
		uncorrected-all           &  -0.75 &  4.62 &             -11.78 &                - \\
		corrected-linear model    &  -0.03 &  0.75 &               0.48 &                2.84 \\
		corrected-quadratic model &  -0.06 &  0.71 &              -0.34 &                2.84 \\
		corrected-cubic model     &  -0.05 &  0.72 &              -0.23 &                2.84 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation (std), and measure of skewness of error
      distributions shown in Figure~\ref{fig:correction:c34-42:fit}. The
      fraction rejected describes the percentage of cases which are removed.
      Results from three different fit models are shown: linear, quadratic and
      cubic.}
	\label{tab:correction:stats:34:42:allfits}
\end{table}
%
\begin{figure}[!tb]
  \centering \includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: noise
      (simulation dataset), uncorrected (thinned measurements), filtered $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are rejected), corrected $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are corrected), corrected
      $2\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 2$\sigma$ are corrected), Sreerekha et al (cloudy cases are filtered according to \citet{rekha2012potential}).}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
	uncorrected     		&  -1.27 &  6.05 &              -8.97 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
	sreerekha et al         &  -0.16 &  0.71 &              -0.46 &               46.37 \\			
		\hline
\end{tabular}
\caption{Bias, standard deviation (std), and measure of skewness of the error
  distributions of datasets shown in
  Figure~\ref{fig:correction:c34-42:thinned}.}
\label{tab:correction:stats:34:42:thinned}
\end{table}

The distributions of filtered data are non-Gaussian. The right side of the
distribution follows measurement noise while the left side is skewed. The
skewness in the distribution is due to cloud impacts which pass through the
clear-sky threshold. The skewness in ``Sreerekha et al'' is higher than our approach because their method only aims at removing cloud impacts above 4\,K. Their approach also leads to a high rejection fraction (46.37\%). The filtering
method introduced here leads to a considerable lower rejection of data
(17.54\%).

@@

Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the
measurements to clear-sky values before and after correction, and the
corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
With clear/cloudy classification for $dtb_{cs} = 1\sigma$, around 85\% of the
total measurements are classified as cloudy and are rejected in pure-filtering.
Rejecting all the cloudy cases reduces the average bias in the measurements
from -2.25\,K to -0.21\,K, while with the approach from
\citet{rekha2012potential} only 46.37\% of the data is rejected and the average
bias reduces to -0.32\,K. When all the cloudy cases, except the ``too cloudy'',
are corrected, the total bias increases to 0.88\,K. The unusually high fraction
of cloudy cases and an increase in bias on correction suggests
misclassification of clear cases as cloudy. Since, the weighting functions of
AWS-32 and AWS-4X are poorly matched, their relationship is inadequate to
estimate the cloud impact in AWS-32. Without any additional information, the
regression approach can only provide a successful filtering in comparison to
the original approach described by \citet{rekha2012potential}, although at the
cost of high rejection fraction. Additional information seems necessary to improve
the accuracy of the correction.

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std & skewness & fraction \\
						&   [K]  &   [K] & [-] 		& rejected [\%]\\
		\hline
Noise             		&  0.00 &  0.45 &               0.01 &                - \\
uncorrected       		&  -2.25 &  8.94 &              -6.85 &                - \\
filtered($1\sigma$)  	&  -0.21 &  0.51 &              -0.65 &               85.43 \\
corrected($1\sigma$) 	&   0.88 &  1.76 &              -1.30 &                5.35 \\
corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.07 &                5.35 \\
sreerekha et al   		&  -0.32 &  0.78 &              -1.94 &               46.37 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for
      channel combinations: AWS-32 and AWS-4X. }
	\label{tab:correction:stats:32:4X}
\end{table}

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std & skewness & fraction \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		noise             		&   0.00 &  0.45 &               0.00 &                - \\
		uncorrected       		&  -2.25 &  8.94 &              -6.85 &                 - \\
		filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.33 &               72.06 \\
		corrected($1\sigma$) 	&   0.43 &  1.70 &             -14.68 &                7.93 \\
		corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.86 &                7.93 \\
		 sreerekha et al   		&  -0.32 &  0.78 &              -1.94 &               46.37 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-32 and AWS-41.   }
	\label{tab:correction:stats:32:41}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &  skewness  & fraction\\
		&   [K]  &   [K] & [-]  & rejected [\%]\\
		\hline
		noise       	    	&  0.00 &  0.45 &               0.00 &               - \\
		uncorrected	    		&  -1.74 &  7.45 &              -7.77 &                - \\
		filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.18 \\
		corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.88 \\
		corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.88 \\
		sreerekha et al         &  -0.23 &  0.65 &              -1.52 &               46.37 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-33 and AWS-41.   }
	\label{tab:correction:stats:33:41}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise           	  &  0.00  &  0.63 &               0.00 &                -\\
		uncorrected     	  &  -0.83 &  4.50 &             -10.85 &                - \\
		filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.30 \\
		corrected($1\sigma$)  &   0.01 &  0.90 &              -1.65 &                2.86 \\
		corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.35 &                2.86 \\
		sreerekha et al       &  -0.11 &  0.67 &              -0.22 &               46.37 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-35 and AWS-43.}
	\label{tab:correction:stats:35:43}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise            	 &  0.00 &  0.88 &              -0.01 &               - \\
		uncorrected      	 &  -0.54 &  3.40 &             -12.26 &                - \\
		filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.38 \\
		corrected($1\sigma$) &  -0.07 &  0.93 &              -0.07 &                2.50 \\
		corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
		sreerekha et al      &  -0.08 &  0.90 &              -0.02 &               46.37 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-36 and AWS-43.   }
	\label{tab:correction:stats:36:43}
\end{table}

@@

Table~\ref{tab:correction:stats:32:41} shows the statistics when AWS-32 is
corrected using AWS-41. The bias and standard deviation of the filtered dataset are better than
the approach by \cite{rekha2012potential}. However, the results from ``sreerekha et al'' have lower skewness. After correction, the corrected data have poorer
statistics. This is not surprising as the weighting function match between
AWS-32 and AWS-41 is poor. The correction using $2\sigma$ as threshold works
better $1\sigma$. This is an exception, the reverse is valid for AWS-34/42 (as
mentioned) and the channel combinations discussed below.
